Graphs for final report

### 2022-08-02 Report/Graphs for final report.Rmd
CARE net income/loss graph.

>>>>

```{r}
care |>
  rename(
    Year = year,
    `Net income` = arsresultat,
    `Net positive` = annual_profit
  ) |>
  ggplot(aes(Year, `Net income`, fill = `Net positive`)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$annual_profit) +
  labs(
    x = "", y = "", title = "Net income (in thousands)"
  ) +
  theme_light() +
  theme(legend.position = "none")
```
